Analysis of split plot design using MCMCglmm

### 2017-04-24 Analysis.Rmd
Formatting in text
Update packages with packrat and revise analysis

---
title: "Analysis"
output: github_document
---

@@

These analyses DO NOT nest the main plot effect as a random effect with the replicate.

@@

@@

trts <-  data.frame(LShB_lmm_2015$Sol[, 2:6])
names(trts)[names(trts) == "WMGTFLD.NRTE100"] <- "FLD.NRTE100"
names(trts)[names(trts) == "WMGTFLD.NRTE120"] <- "FLD.NRTE120"
trts <- melt(trts)

@@

trts <-  data.frame(TShB_severity_lmm_2015$Sol[, 2:6])
names(trts)[names(trts) == "WMGTFLD.NRTE100"] <- "FLD.NRTE100"
names(trts)[names(trts) == "WMGTFLD.NRTE120"] <- "FLD.NRTE120"
trts <- melt(trts)

@@

trts <-  data.frame(TShB_incidence_lmm_2015$Sol[, 2:6])
names(trts)[names(trts) == "WMGTFLD.NRTE100"] <- "FLD.NRTE100"
names(trts)[names(trts) == "WMGTFLD.NRTE120"] <- "FLD.NRTE120"
trts <- melt(trts)

@@

trts <-  data.frame(LShB_lmm_2016$Sol[, 2:4])
names(trts)[names(trts) == "WMGTFLD.NRTE180"] <- "FLD.NRTE180"
trts <- melt(trts)

@@

trts <-  data.frame(TShB_severity_lmm_2016$Sol[, 2:4])
names(trts)[names(trts) == "WMGTFLD.NRTE180"] <- "FLD.NRTE180"
trts <- melt(trts)

@@

trts <-  data.frame(TShB_incidence_lmm_2016$Sol[, 2:4])
names(trts)[names(trts) == "WMGTFLD.NRTE100"] <- "FLD.NRTE100"
names(trts)[names(trts) == "WMGTFLD.NRTE120"] <- "FLD.NRTE120"
trts <- melt(trts)

>>>>

---
title: "Analysis of split plot design using MCMCglmm"
output: github_document
---

@@

@@

## Setup
Use `set.seed()` for reproducibility.

```{r set_seed}
set.seed(27)
```

@@

trts <-  data.frame(LShB_lmm_2015$Sol[, 2:6])
trts <- melt(trts)

@@

trts <-  data.frame(TShB_severity_lmm_2015$Sol[, 2:6])
trts <- melt(trts)

@@

trts <-  data.frame(TShB_incidence_lmm_2015$Sol[, 2:6])
trts <- melt(trts)

@@

trts <-  data.frame(LShB_lmm_2016$Sol[, 2:4])
trts <- melt(trts)

@@

trts <-  data.frame(TShB_severity_lmm_2016$Sol[, 2:4])
trts <- melt(trts)

@@

trts <-  data.frame(TShB_incidence_lmm_2016$Sol[, 2:4])
trts <- melt(trts)
